\documentclass[12pt]{report}
%\usepackage{amsmath}   
\usepackage[margin=0.25in]{geometry}        % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}          % ... or a4paper or a5paper or ... 
%\usepackage{textcomp}
%\usepackage{graphicx}
\usepackage{hyperref}
%\usepackage{amssymb}
%\usepackage{epstopdf}
%\usepackage{verbatim}
%\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{wrapfig}
%\usepackage{setspace}
%\usepackage{fancyhdr}
\usepackage{framed}
\usepackage{color}
\usepackage{calc}
%\usepackage{fontspec}
\pagestyle{empty}

% define some colors
\definecolor{MidnightBlue}{RGB}{25,25,112}
\definecolor{White}{RGB}{255,255,255}

\hypersetup{
colorlinks=true,
urlcolor=blue
}

\newcommand{\TopBox}{
\noindent\colorbox{MidnightBlue}{%
\noindent\parbox{8.0in}{\textcolor{White}{%
\begin{center}
\vspace{0.0625in}
\noindent {Computer Programming $|$ Web Technologies $|$ Database Management $|$ Software Engineering}
\vspace{0.0625in}
\end{center}
}}}
}

\newcommand{\BottomBox}{
\noindent\colorbox{MidnightBlue}{%
\noindent\parbox{8.0in}{\textcolor{White}{%
\begin{center}
\vspace{0.0625in}
\noindent {Trevor Daniels, 125 Cambon Drive Apt 12-K -- San Francisco, CA 94132}
\vspace{0.0625in}
\end{center}
}}}
}

%\setsansfont{Nimbus Sans L}

\begin{document}

% top blue box
\TopBox

% my name and contact info
\begin{center}
\noindent {\Huge \textsf{Trevor Daniels}} \\
\noindent\textsf{rm.trev@gmail.com $|$ 402.770.0975}
\end{center}

% create a parbox to have 1 inch margins
\begin{center}
\noindent\parbox{6.5in}{{\small
\noindent \framebox[6.5in][l]{\large\textbf{\textit{Skills}}}
\begin{itemize}
\item Over fifteen years experience with the GNU/Linux toolchain.
\item Six years experience with NodeJs.
\item Knowledgeable with Docker and is able to deploy containerized applications using Docker Compose.
\item Automated testing purist; Aggressively tests at the unit level with Mocha and Sinon, and at the Component-to-End level with Cucumber.
%\item Proficient with Android development. Built a client-server data synchronization system for a data collection app, meant to address the issue of limited network connectivity in rural Nebraska.
%\item Experience with heuristic-driven search algorithms, such as A$\ast$, used in artificial intelligence.
\item Ability to work in an agile environment to complete software development projects.
\end{itemize}
}}

\noindent\parbox{6.5in}{{\small
\noindent\framebox[6.5in][l]{\large\textbf{\textit{Technical Tools}}}
\begin{itemize}
\item\textbf{Languages:} ECMAScript 6, Typescript, C\#, Python, Java, HTML5, CSS3
\item\textbf{Database Engines:} PostgreSQL, MySQL, MSSQL, SQLite, CouchDB
\item\textbf{Development Environments:} WebStorm, Visual Studio, Eclipse, Android SDK, Emacs
\item\textbf{Frameworks:} NodeJs, Angular, React, Vue, .NET, Django, jQuery, LESS, SASS
\item\textbf{Testing Frameworks:} Jest, Sinon, Mocha, Cucumber
\item\textbf{Source Control:} Git, Team Foundation Server
\item\textbf{DevOps Tools:} Docker, Terraform
\item\textbf{Documentation Tools:} Markdown, Mermaid
\end{itemize}
}}

\noindent\parbox{6.5in}{{\small
\noindent \framebox[6.5in][l]{\large\textbf{\textit{Education}}}
\begin{itemize}
\item\textbf{University of Nebraska--Lincoln (UNL)}, \textit{College of Arts and Sciences}\\
\underline{Lincoln, Nebraska}, January, 2007 -- December, 2011 
\begin{itemize}
\item Graduated December, 2011
\item Computer Science Major, Japanese \& Mathematics Minor
\end{itemize}
\item\textbf{Southeast Community College (SCC)}, \textit{Computer Programming Technology}\\
\underline{Milford, Nebraska}, January, 2005 -- June, 2006
\begin{itemize}
\item Graduated June, 2006
\item Associates of Applied Science
\item Dean's List all quarters
\end{itemize}
\end{itemize}
}}

\vfill
\BottomBox

\newpage
\TopBox

\vspace{0.25in}
\noindent\parbox{6.5in}{{\small
\noindent \framebox[6.5in][l]{\large\textbf{\textit{Professional Experience}}}
\begin{itemize}

\item\textbf{TomoCredit}\\
\textit{Senior Software Engineer}, September, 2021 -- February, 2023
\begin{itemize}
\item Developed and maintained complex features that have a high business impact in an Agile team.
\item Proven work experience as a back-end developer, using languages like JavaScript and TypeScript.
\item Used technologies such as AWS Lambda to create robust, error resistant features.
\item Used automated testing frameworks such as Jest to ensure code reliability.
\end{itemize}

\item\textbf{Globant (formerly PointSource, LLC)}\\
\textit{Junior Software Engineer $\to$ Senior Software Engineer}, August, 2016 -- September, 2021
\begin{itemize}
\item Developed custom web applications for clients, using technologies such as Angular, Vue and NodeJS in an Agile team.
\item Used the Contentful headless CMS alongside Vue to rapidly construct a website for a client.
\item Enforced a very high standard of quality in projects through unit tests, component tests, C2E tests, and code reviews.
\item Has experience in code optimization, both front-end and back-end.
\item Additional experience includes building a prototype mobile app using Angular, Cordova, and responsive design.
\end{itemize}

\item\textbf{GIS Workshop, LLC}\\
\textit{Software Developer}, May, 2012 -- January, 2016
\begin{itemize}
\item Developed custom GIS solutions for a variety of platforms, including desktop, web and Android, using ESRI's ArcGIS as the underlying engine.
\item Managed websites for hundreds of clients, primarily county officials across Nebraska, North Dakota, and South Dakota.
\item Maintained custom websites on an individual basis with clients. Websites have special features such as document management and custom queries.
\item Website front-ends implemented using a variety of frameworks, including HTML5, Adobe Flex, and Silverlight using Windows Presentation Foundation.
\end{itemize}

%\item\textbf{UNL Student Involvement--Information Strategies}\\
%\textit{Webmaster/Database Manager}, January, 2007 -- December, 2011
%\begin{itemize}
%\item Managed and updated three websites with seven different program areas.
%\item Designed, produced and uploaded Flash and other multimedia promotions for all Student Involvement events and programs.
%\item Worked within a team setting to create web and multimedia promotional materials and web forms that are %effective for college students.
%\item Created web applications using PHP and Django Framework to assist students.
%%\item Worked with databases, clients and server-side scripting.
%\end{itemize}

%\item\textbf{Southeast Community College--Technology}\\
%\textit{Student IT Technician}, Summer 2006
%\begin{itemize}
%\item Assisted in rewiring SCC's computer network.
%\item Handled and terminated Ethernet and fiber optic cables.
%\item Charged with setting up all new lab computers.
%\end{itemize}

\end{itemize}
}}

\noindent\parbox{6.5in}{{\small
\noindent \framebox[6.5in][l]{\large\textbf{\textit{Links}}}
\begin{itemize}
\item\textbf{Github:} \href{https://github.com/RMTrev}{https://github.com/RMTrev}
\item\textbf{LinkedIn:} \href{https://www.linkedin.com/in/trevor-daniels-72bb078}{https://www.linkedin.com/in/trevor-daniels-72bb078}
\end{itemize}
}}

%\noindent\textbf{\textit{References available upon request}}
\end{center}

\vfill

% bottom blue box
\BottomBox

\end{document}
